---
title: '1986 ANES Analysis: 11/17 Update'
author: "Mark Weiss to Don Kinder"
date: "November 17, 2023"
output:
  pdf_document: default
  toc: yes
  theme: united
  html_document: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preliminaries
Last time I checked in, parts 3 and 4 produced results that were inconsistent with 
previous analyses on similar datasets. I believe I've figured out the problem.

```{r, results='hide', message = FALSE, error = FALSE, echo = FALSE}
# ==================================================================
# I: Load packages, import data and define variables of interest
# ==================================================================

# clear global environment and set working directory
rm(list = ls())
setwd("/Users/markweiss/Dropbox/Mac (2)/Documents/Research/Projects/kinder_ra/data")

# install packages
install_pack <- function(pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if(length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

packages <- c("dplyr", "readr", "tidycensus", "knitr", "haven","aod")
install_pack(packages)

# import data
mydata <- read_dta("nes1986.dta")

# rename important vars
mydata <- mydata %>% 
  rename("form" = V860046, 
         "sex" = V860755, 
         "race" = V860756, 
         "hispanic" = V860757, 
         "education" = V860599,  
         "rent_own" = V860754, 
         "try_harder" = V860579, 
         "slvry_blame" = V860580, 
         "less_deserve" = V860566, 
         "overc_prej" = V860568, 
         "know_bush" = V860343,
         "know_weinberger" = V860344,
         "know_rehnquist" = V860345, 
         "know_volker" = V860346, 
         "know_dole" = V860347, 
         "know_oneill" = V860348,
         "interest_1" = V860102, 
         "interest_2" = V860059,
         "party_id" = V860300, 
         "govt_services" = V860448, 
         "coop_russia" = V860487, 
         "import_restr" = V860520, 
         "defense_spend" = V860405, 
         "interv_ca" = V860428, 
         "hear_africa" = V860489, 
         "africa_sanct" = V860490, 
         "eq_opp_succeed" = V860364, 
         "eq_rights_toofar" = V860365, 
         "dont_give_eqchance" = V860366, 
         "worried_less_eq" = V860367, 
         "treateq_few_prob" = V860369,
         "africa_strength" = V860491
  )

# classify form A and B
mydata$form_a <- ifelse(mydata$form %in% c(1, 4), 1, 0)
mydata$form_b <- ifelse(mydata$form %in% c(2, 3), 1, 0)

# define demographic/socioeconomic variables
mydata$white <- rep(NA, nrow(mydata))
mydata$black <- rep(NA, nrow(mydata))

mydata$nhs <- rep(NA, nrow(mydata))
mydata$hs <- rep(NA, nrow(mydata))
mydata$somecol <- rep(NA, nrow(mydata))
mydata$college <- rep(NA, nrow(mydata))
mydata$less_hs <- rep(NA, nrow(mydata))
mydata$some_postcol <- rep(NA, nrow(mydata))
mydata$postgrad <- rep(NA, nrow(mydata))
mydata$own <- rep(NA, nrow(mydata))

mydata$op_africa <- rep(NA, nrow(mydata))
mydata$sanctions <- rep(NA, nrow(mydata))
mydata$op_govt_services <- rep(NA, nrow(mydata))
mydata$op_coop_russia <- rep(NA, nrow(mydata))
mydata$op_defense_spend <- rep(NA, nrow(mydata))
mydata$op_interv_ca <- rep(NA, nrow(mydata))
mydata$op_import_restr <- rep(NA, nrow(mydata))

mydata$egal <- rep(NA, nrow(mydata))

# ==================================================================
# II: Code outcomes and covariates of interest
# ==================================================================

# code demographic vars
mydata <- mydata %>%
  mutate(
    white = ifelse(between(race, 1, 4) & race != 99, 0, white),
    white = ifelse(race == 1 & hispanic == 5 & race != 99, 1, white),
    black = ifelse(race == 2, 1, ifelse(race == 1 | race > 2, 0, black)),
    female = ifelse(sex == 2, 0, 1),
    sex = ifelse(sex == 2, 0, ifelse(sex == 1, 1, NA))
  ) 

# code socioeconomic vars
mydata <- mydata %>%
  mutate(
    nhs = case_when(
    education < 12 ~ 1,
    education >= 12 & education != 99 ~ 0,
    TRUE ~ NA_real_
  ),
  hs = case_when(
    education == 12 ~ 1,
    education < 12 | (education > 12 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  somecol = case_when(
    between(education, 13, 15) ~ 1,
    education < 12 | (education > 15 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  college = case_when(
    education == 16 ~ 1,
    education < 16 | (education > 16 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  less_hs = case_when(
    education < 12 ~ 1, 
    education >= 12 & education != 99 ~ 0, 
    education == 99 ~ NA_real_
  ),
  some_postcol = case_when(
    between(education, 13, 15) ~ 1,
    education < 12 | (education > 15 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ))

mydata <- mydata %>%
  mutate(own = case_when(
    rent_own == 1 ~ 1,
    rent_own %in% 2:7 ~ 0,
    TRUE ~ NA_real_
  ))

# identify political figure vars
names <- c("bush", "weinberger", "rehnquist", "volker", "dole", "oneill")

mydata <- mydata %>%
  mutate(across(starts_with("know"), ~ ifelse(. == 1, 1, ifelse(. %in% c(5, 8), 0, NA)), .names = "ident_{.col}")) %>%
  select(-starts_with("know")) %>%
  rename(
    "ident_bush" = ident_know_bush, 
    "ident_weinberger" = ident_know_weinberger, 
    "ident_rehnquist" = ident_know_rehnquist, 
    "ident_volker" = ident_know_volker, 
    "ident_dole" = ident_know_dole,
    "ident_oneill" = ident_know_oneill
  )

mydata$knowledge <- rowMeans(mydata[, c("ident_bush", "ident_weinberger",
                                        "ident_rehnquist", "ident_volker", "ident_dole", "ident_oneill")])

# interest in politics variables
mydata <- mydata %>%
  mutate(interest_1 = case_when(
    interest_1 == 1 ~ 0.5,
    interest_1 == 2 ~ 0.334,
    interest_1 == 4 ~ 0.167,
    interest_1 == 5 ~ 0,
    interest_1 %in% c(8, 9) ~ NA_real_,
    TRUE ~ interest_1
  )) %>%
  mutate(interest_2 = case_when(
    interest_2 == 1 ~ 0.5,
    interest_2 == 3 ~ 0.334,
    interest_2 == 5 ~ 0.167,
    interest_2 == 9 ~ NA_real_,
    TRUE ~ interest_2
  ))

mydata$taste <- rowSums((mydata[, c("interest_1", "interest_2")]))

# modern racism variable
# overc_prej, slvr_blame, less_deserve, try_harder

mydata <- mydata %>%
  mutate(overc_prej = case_when( 
    overc_prej %in% c(0, 8, 9) ~ NA_real_,
    overc_prej == 1 ~ 1, 
    overc_prej == 2 ~ 0.5, 
    overc_prej == 3 ~ 0,
    overc_prej == 4 ~ -0.5, 
    overc_prej == 5 ~ -1,
  )) %>%
  mutate(try_harder = case_when(
    try_harder %in% c(0, 8, 9) ~ NA_real_,
    try_harder == 1 ~ 1, 
    try_harder == 2 ~ 0.5, 
    try_harder == 3 ~ 0, 
    try_harder == 4 ~ -0.5,
    try_harder == 5 ~ -1
  )) %>%
  mutate(slvry_blame = case_when(
    slvry_blame %in% c(0, 8, 9) ~ NA_real_, 
    slvry_blame == 1 ~ -1, 
    slvry_blame == 2 ~ -0.5, 
    slvry_blame == 3 ~ 0, 
    slvry_blame == 4 ~ 0.5, 
    slvry_blame == 5 ~ 1 
  )) %>%
  mutate(less_deserve = case_when(
    less_deserve %in% c(0, 8, 9) ~ NA_real_, 
    less_deserve == 1 ~ -1, 
    less_deserve == 2 ~ -0.5, 
    less_deserve == 3 ~ 0, 
    less_deserve == 4 ~ 0.5, 
    less_deserve == 5 ~ 1
  ))

mydata$racism <- rowMeans(mydata[, c("overc_prej", "try_harder", "slvry_blame", "less_deserve")])

# partisanship variable
mydata <- mydata %>%
  mutate(party_id = case_when( 
    party_id %in% c(7:9) ~ NA_real_,
    party_id == 0 ~ -1, 
    party_id == 1 ~ -0.666, 
    party_id == 2 ~ -0.333, 
    party_id == 3 ~ 0, 
    party_id == 4 ~ 0.333, 
    party_id == 5 ~ 0.666, 
    party_id == 6 ~ 1))

# two primary dep. vars - opinion on Africa sanctions and actual opinon
## know_africa = binary for whether one takes a position on Africa sanctions
## africa_sanct = actual opinion on Sanctions
mydata <- mydata %>%
  mutate(op_africa = case_when(
    hear_africa == 1 ~ 1,
    hear_africa == 9 ~ NA_real_,
    hear_africa %in% c(5,8) ~ 0
  )) %>% 
  mutate(sanctions = case_when( 
    africa_strength == 1 ~ 1, 
    africa_strength == 2 ~ 0.5, 
    africa_strength == 4 ~ -0.5,
    africa_strength == 5 ~ -1,
    africa_strength %in% c(4,8,0) ~ NA_real_
  ))
table(mydata$op_africa)

# takes opinion on alternate dep. variabless
mydata <- mydata %>%
  mutate(op_govt_services = case_when( 
    govt_services == 9 ~ NA_real_, 
    govt_services %in% c(0,8) ~ 0, 
    govt_services %in% c(1:7) ~ 1
  )) %>%
  mutate(op_import_restr = ifelse(mydata$import_restr == 1, 1, 
                                  ifelse(mydata$import_restr %in% c(5, 8), 0, NA))) %>%
  mutate(op_coop_russia = case_when(
    coop_russia == 9 ~ NA_real_,
    coop_russia %in% c(0,8) ~ 0, 
    coop_russia %in% c(1:7) ~ 1
  )) %>%
  mutate(op_defense_spend = case_when(
    defense_spend == 9 ~ NA_real_,
    defense_spend %in% c(0,8) ~ 0, 
    defense_spend %in% c(1:7) ~ 1
  )) %>%
  mutate(op_interv_ca = case_when( 
    interv_ca == 9 ~ NA_real_,
    interv_ca %in% c(0,8) ~ 0, 
    interv_ca %in% c(1:7) ~ 1
  ))

# egalitarian variable
mydata <- mydata %>%
  mutate(eq_opp_succeed = case_when( 
    eq_opp_succeed == 1 ~ 1, 
    eq_opp_succeed == 2 ~ 0.5, 
    eq_opp_succeed == 3 ~ 0, 
    eq_opp_succeed == 4 ~ -0.5, 
    eq_opp_succeed == 5 ~ -1, 
    eq_opp_succeed %in% c(8,9) ~ NA_real_
  )) %>%
  mutate(dont_give_eqchance = case_when( 
    dont_give_eqchance == 1 ~ 1, 
    dont_give_eqchance == 2 ~ 0.5, 
    dont_give_eqchance == 3 ~ 0, 
    dont_give_eqchance == 4 ~ -0.5, 
    dont_give_eqchance == 5 ~ -1, 
    dont_give_eqchance %in% c(8,9) ~ NA_real_
  )) %>% 
  mutate(treateq_few_prob = case_when( 
    treateq_few_prob == 1 ~ 1, 
    treateq_few_prob == 2 ~ 0.5, 
    treateq_few_prob == 3 ~ 0, 
    treateq_few_prob == 4 ~ -0.5, 
    treateq_few_prob == 5 ~ -1, 
    treateq_few_prob %in% c(8,9) ~ NA_real_
  )) %>%
  mutate(eq_rights_toofar = case_when(
    eq_rights_toofar == 1 ~ -1, 
    eq_rights_toofar == 2 ~ -0.5, 
    eq_rights_toofar == 3 ~ 0, 
    eq_rights_toofar == 4 ~ 0.5, 
    eq_rights_toofar == 5 ~ 1, 
    eq_rights_toofar %in% c(8,9) ~ NA_real_
  )) %>% 
  mutate(worried_less_eq = case_when( 
    worried_less_eq == 1 ~ -1, 
    worried_less_eq == 2 ~ -0.5, 
    worried_less_eq == 3 ~ 0, 
    worried_less_eq == 4 ~ 0.5, 
    worried_less_eq == 5 ~ 1, 
    worried_less_eq %in% c(8,9) ~ NA_real_
    
  ))

mydata$egal <- rowMeans(mydata[, c("worried_less_eq", "eq_rights_toofar", 
                                   "treateq_few_prob", "dont_give_eqchance", "eq_opp_succeed")])

```
```{r, echo = FALSE}
# two primary dep. vars - opinion on Africa sanctions and actual opinon
## know_africa = binary for whether one takes a position on Africa sanctions
## africa_sanct = actual opinion on Sanctions

# takes opinion on alternate dep. variables
mydata <- mydata %>%
    mutate(op_govt_services = case_when( 
      govt_services == 9 ~ NA_real_, 
      govt_services %in% c(0,8) ~ 0, 
      govt_services %in% c(1:7) ~ 1
    )) %>%
    mutate(op_import_restr = ifelse(mydata$import_restr == 1, 1, 
    ifelse(mydata$import_restr %in% c(5, 8), 0, NA))) %>%
    mutate(op_coop_russia = case_when(
      coop_russia == 9 ~ NA_real_,
      coop_russia %in% c(0,8) ~ 0, 
      coop_russia %in% c(1:7) ~ 1
    )) %>%
    mutate(op_defense_spend = case_when(
      defense_spend == 9 ~ NA_real_,
      defense_spend %in% c(0,8) ~ 0, 
      defense_spend %in% c(1:7) ~ 1
    )) %>%
    mutate(op_interv_ca = case_when( 
      interv_ca == 9 ~ NA_real_,
      interv_ca %in% c(0,8) ~ 0, 
      interv_ca %in% c(1:7) ~ 1
    ))

```

```{R eval=FALSE, include=FALSE}
# generate summary statistics
alt_dep <- c("op_govt_services","op_import_restr","op_defense_spend","op_interv_ca","op_coop_russia")
summary_stats <- lapply(mydata[alt_dep], summary)
frequencies <- lapply(mydata[alt_dep], table)

# print summary statistics
for (i in seq_along(summary_stats)) {
  cat("Frequencies for", alt_dep[i], ":\n")
  print(frequencies[i])
  cat("\n")
  
  cat("Summary Statistics for", alt_dep[i], ":\n")
  print(summary_stats[i])
  cat("\n")
}

```

### 1) Opinion on sanctions, non-hispanic whites
```{r}
# non-hispanic whites, form A
white_form_a <- mydata %>% filter(white == 1 & form_a == 1)
table(white_form_a$sanctions)

# whites, formed an opinion = 1, haven't = 0, form B
table(white_form_a$op_africa)

# non-hispanic whites, form B
white_form_b <- mydata %>% filter(white == 1 & form_b == 1)
table(white_form_b$sanctions)

# whites, formed an opinion = 1, haven't = 0, form B
table(white_form_b$op_africa)

# non-hispanic whites, form A and B
white_both_forms <- mydata %>% filter(white == 1)
table(white_both_forms$sanctions)

# whites, formed an opinion = 1, haven't = 0, form A+B
table(white_both_forms$op_africa)
```

### 2) Frequencies for Black Americans
```{r}
# Black Americans, form A
black_form_a <- mydata %>% filter(black == 1 & form_a == 1)
table(black_form_a$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form A
table(black_form_a$op_africa)

# Black Americans, form B
black_form_b <- mydata %>% filter(black == 1 & form_b == 1)
table(black_form_b$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form B
table(black_form_b$op_africa)

# Black Americans, form A and B
black_both_forms <- mydata %>% filter(black == 1)
table(black_both_forms$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form A+B
table(black_both_forms$op_africa)

```

### 3) Accounting for No Opinion Model
**Non-hispanic whites, form A and B**
```{r, echo=FALSE}
# create models for all specifications 
part3_1 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_both_forms)
part3_2 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_form_a)
part3_3 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_form_b)
part3_4 <-  glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = black_both_forms)
summary(part3_1)

```
**Non-hispanic whites, form A**
```{r, echo=FALSE}
summary(part3_2)
```
**Non-hispanic whites, form B**
```{r, echo=FALSE}
summary(part3_3)
```
**Black Americans, forms A and B**
```{r, echo=FALSE}
summary(part3_4)
```

### 4) Accounting for no opinion with racial resentment
```{r}
part4_1 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = white_form_b)
summary(part4_1)
```

### 5) Identical model, alternative outcomes
```{r, echo = FALSE}
part5_1 <- glm(op_defense_spend ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_2 <- glm(op_interv_ca ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_3 <- glm(op_govt_services ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_4 <- glm(op_coop_russia ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_5 <- glm(op_import_restr ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
```
**Defense spending:**
```{r}
summary(part5_1)
```
**Intervention in Central America:**
```{r}
summary(part5_2)
```
**Government services/cuts in spending:**
```{r}
summary(part5_3)
```
**Cooperate with Russia:**
```{r}
summary(part5_4)
```
**Import Restrictions:**
```{r}
summary(part5_5)
```
