########################################################################################
# This file contains all of the work completed by Mark Weiss as an RA for Donald Kinder.
# Last updated 12/22/2023 by Mark Weiss
########################################################################################
---
title: '1986 ANES Analysis: Parts 1-7'
author: "Mark Weiss to Don Kinder"
date: "December 22, 2023"
output:
  pdf_document: default
  toc: yes
  theme: united
  html_document: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide', message = FALSE, error = FALSE, echo = FALSE}
# ==================================================================
# I: Load packages, import data and define variables of interest
# ==================================================================

# clear global environment and set working directory
rm(list = ls())
setwd("/Users/markweiss/Dropbox/Mac (2)/Documents/Research/Projects/kinder_ra/data")

# install packages
install_pack <- function(pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if(length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

packages <- c("dplyr", "readr", "tidycensus", "knitr", "haven","aod","psych",
              "gmodels","ggplot2")
install_pack(packages)

# import data
mydata <- read_dta("nes1986.dta")

# rename important vars
mydata <- mydata %>% 
  rename("form" = V860046, 
         "sex" = V860755, 
         "race" = V860756, 
         "hispanic" = V860757, 
         "education" = V860599,  
         "rent_own" = V860754, 
         "try_harder" = V860579, 
         "slvry_blame" = V860580, 
         "less_deserve" = V860566, 
         "overc_prej" = V860568, 
         "know_bush" = V860343,
         "know_weinberger" = V860344,
         "know_rehnquist" = V860345, 
         "know_volker" = V860346, 
         "know_dole" = V860347, 
         "know_oneill" = V860348,
         "interest_1" = V860102, 
         "interest_2" = V860059,
         "party_id" = V860300, 
         "govt_services" = V860448, 
         "coop_russia" = V860487, 
         "import_restr" = V860520, 
         "defense_spend" = V860405, 
         "interv_ca" = V860428, 
         "hear_africa" = V860489, 
         "africa_sanct" = V860490, 
         "eq_opp_succeed" = V860364, 
         "eq_rights_toofar" = V860365, 
         "dont_give_eqchance" = V860366, 
         "worried_less_eq" = V860367, 
         "treateq_few_prob" = V860369,
         "bigprob" = V860368,
         "africa_strength" = V860491,
         "racism_bio" = V860582,
         "integration" = V860485,
         "int_op" = V860484,
         "workplace_op" = V860469,
         "workplace" = V860470,
         "effort_poc" = V860426,
         "effort_black" = V860427
  )

# classify form A and B
mydata$form_a <- ifelse(mydata$form %in% c(1, 4), 1, 0)
mydata$form_b <- ifelse(mydata$form %in% c(2, 3), 1, 0)

# define demographic/socioeconomic variables
mydata$white <- rep(NA, nrow(mydata))
mydata$black <- rep(NA, nrow(mydata))

mydata$nhs <- rep(NA, nrow(mydata))
mydata$hs <- rep(NA, nrow(mydata))
mydata$somecol <- rep(NA, nrow(mydata))
mydata$college <- rep(NA, nrow(mydata))
mydata$less_hs <- rep(NA, nrow(mydata))
mydata$some_postcol <- rep(NA, nrow(mydata))
mydata$postgrad <- rep(NA, nrow(mydata))
mydata$own <- rep(NA, nrow(mydata))

mydata$op_africa <- rep(NA, nrow(mydata))
mydata$sanctions <- rep(NA, nrow(mydata))
mydata$op_govt_services <- rep(NA, nrow(mydata))
mydata$op_coop_russia <- rep(NA, nrow(mydata))
mydata$op_defense_spend <- rep(NA, nrow(mydata))
mydata$op_interv_ca <- rep(NA, nrow(mydata))
mydata$op_import_restr <- rep(NA, nrow(mydata))

mydata$egal <- rep(NA, nrow(mydata))

# ==================================================================
# II: Code outcomes and covariates of interest
# ==================================================================

# code demographic vars
mydata <- mydata %>%
  mutate(
    white = ifelse(between(race, 1, 4) & race != 99, 0, white),
    white = ifelse(race == 1 & hispanic == 5 & race != 99, 1, white),
    black = ifelse(race == 2, 1, ifelse(race == 1 | race > 2, 0, black)),
    female = ifelse(sex == 2, 0, 1),
    sex = ifelse(sex == 2, 0, ifelse(sex == 1, 1, NA))
  ) 

# code socioeconomic vars
mydata <- mydata %>%
  mutate(
    nhs = case_when(
    education < 12 ~ 1,
    education >= 12 & education != 99 ~ 0,
    TRUE ~ NA_real_
  ),
  hs = case_when(
    education == 12 ~ 1,
    education < 12 | (education > 12 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  somecol = case_when(
    between(education, 13, 15) ~ 1,
    education < 12 | (education > 15 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  college = case_when(
    education == 16 ~ 1,
    education < 16 | (education > 16 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ),
  less_hs = case_when(
    education < 12 ~ 1, 
    education >= 12 & education != 99 ~ 0, 
    education == 99 ~ NA_real_
  ),
  some_postcol = case_when(
    between(education, 13, 15) ~ 1,
    education < 12 | (education > 15 & education != 99) ~ 0,
    TRUE ~ NA_real_
  ))

mydata <- mydata %>%
  mutate(own = case_when(
    rent_own == 1 ~ 1,
    rent_own %in% 2:7 ~ 0,
    TRUE ~ NA_real_
  ))

# identify political figure vars
names <- c("bush", "weinberger", "rehnquist", "volker", "dole", "oneill")

mydata <- mydata %>%
  mutate(across(starts_with("know"), ~ ifelse(. == 1, 1, ifelse(. %in% c(5, 8), 0, NA)), .names = "ident_{.col}")) %>%
  select(-starts_with("know")) %>%
  rename(
    "ident_bush" = ident_know_bush, 
    "ident_weinberger" = ident_know_weinberger, 
    "ident_rehnquist" = ident_know_rehnquist, 
    "ident_volker" = ident_know_volker, 
    "ident_dole" = ident_know_dole,
    "ident_oneill" = ident_know_oneill
  )

mydata$knowledge <- rowMeans(mydata[, c("ident_bush", "ident_weinberger",
                                        "ident_rehnquist", "ident_volker", "ident_dole", "ident_oneill")])

# interest in politics variables
mydata <- mydata %>%
  mutate(interest_1 = case_when(
    interest_1 == 1 ~ 0.5,
    interest_1 == 2 ~ 0.334,
    interest_1 == 4 ~ 0.167,
    interest_1 == 5 ~ 0,
    interest_1 %in% c(8, 9) ~ NA_real_,
    TRUE ~ interest_1
  )) %>%
  mutate(interest_2 = case_when(
    interest_2 == 1 ~ 0.5,
    interest_2 == 3 ~ 0.334,
    interest_2 == 5 ~ 0.167,
    interest_2 == 9 ~ NA_real_,
    TRUE ~ interest_2
  ))

mydata$taste <- rowSums((mydata[, c("interest_1", "interest_2")]))

# modern racism variable
# overc_prej, slvr_blame, less_deserve, try_harder

mydata <- mydata %>%
  mutate(overc_prej = case_when( 
    overc_prej %in% c(0, 8, 9) ~ NA_real_,
    overc_prej == 1 ~ 1, 
    overc_prej == 2 ~ 0.5, 
    overc_prej == 3 ~ 0,
    overc_prej == 4 ~ -0.5, 
    overc_prej == 5 ~ -1,
  )) %>%
  mutate(try_harder = case_when(
    try_harder %in% c(0, 8, 9) ~ NA_real_,
    try_harder == 1 ~ 1, 
    try_harder == 2 ~ 0.5, 
    try_harder == 3 ~ 0, 
    try_harder == 4 ~ -0.5,
    try_harder == 5 ~ -1
  )) %>%
  mutate(slvry_blame = case_when(
    slvry_blame %in% c(0, 8, 9) ~ NA_real_, 
    slvry_blame == 1 ~ -1, 
    slvry_blame == 2 ~ -0.5, 
    slvry_blame == 3 ~ 0, 
    slvry_blame == 4 ~ 0.5, 
    slvry_blame == 5 ~ 1 
  )) %>%
  mutate(less_deserve = case_when(
    less_deserve %in% c(0, 8, 9) ~ NA_real_, 
    less_deserve == 1 ~ -1, 
    less_deserve == 2 ~ -0.5, 
    less_deserve == 3 ~ 0, 
    less_deserve == 4 ~ 0.5, 
    less_deserve == 5 ~ 1
  ))

mydata$racism <- rowMeans(mydata[, c("overc_prej", "try_harder", "slvry_blame", "less_deserve")])

# partisanship variable
mydata <- mydata %>%
  mutate(party_id = case_when( 
    party_id %in% c(7:9) ~ NA_real_,
    party_id == 0 ~ -1, 
    party_id == 1 ~ -0.666, 
    party_id == 2 ~ -0.333, 
    party_id == 3 ~ 0, 
    party_id == 4 ~ 0.333, 
    party_id == 5 ~ 0.666, 
    party_id == 6 ~ 1))

# two primary dep. vars - opinion on Africa sanctions and actual opinon
## know_africa = binary for whether one takes a position on Africa sanctions
## africa_sanct = actual opinion on Sanctions
mydata <- mydata %>%
  mutate(op_africa = case_when(
    hear_africa == 1 ~ 1,
    hear_africa == 9 ~ NA_real_,
    hear_africa %in% c(5,8) ~ 0
  )) %>% 
  mutate(sanctions = case_when( 
    africa_strength == 1 ~ 1, 
    africa_strength == 2 ~ 0.666, 
    africa_strength == 4 ~ 0.333,
    africa_strength == 5 ~ 0,
    africa_strength %in% c(4,8,0) ~ NA_real_
  ))
table(mydata$op_africa)

# takes opinion on alternate dep. variables
mydata <- mydata %>%
  mutate(op_govt_services = case_when( 
    govt_services == 9 ~ NA_real_, 
    govt_services %in% c(0,8) ~ 0, 
    govt_services %in% c(1:7) ~ 1
  )) %>%
  mutate(op_import_restr = ifelse(mydata$import_restr == 1, 1, 
                                  ifelse(mydata$import_restr %in% c(5, 8), 0, NA))) %>%
  mutate(op_coop_russia = case_when(
    coop_russia == 9 ~ NA_real_,
    coop_russia %in% c(0,8) ~ 0, 
    coop_russia %in% c(1:7) ~ 1
  )) %>%
  mutate(op_defense_spend = case_when(
    defense_spend == 9 ~ NA_real_,
    defense_spend %in% c(0,8) ~ 0, 
    defense_spend %in% c(1:7) ~ 1
  )) %>%
  mutate(op_interv_ca = case_when( 
    interv_ca == 9 ~ NA_real_,
    interv_ca %in% c(0,8) ~ 0, 
    interv_ca %in% c(1:7) ~ 1
  ))

# egalitarian variable
mydata <- mydata %>%
  mutate(eq_opp_succeed = case_when( 
    eq_opp_succeed == 1 ~ 1, 
    eq_opp_succeed == 2 ~ 0.5, 
    eq_opp_succeed == 3 ~ 0, 
    eq_opp_succeed == 4 ~ -0.5, 
    eq_opp_succeed == 5 ~ -1, 
    eq_opp_succeed %in% c(8,9) ~ NA_real_
  )) %>%
  mutate(dont_give_eqchance = case_when( 
    dont_give_eqchance == 1 ~ 1, 
    dont_give_eqchance == 2 ~ 0.5, 
    dont_give_eqchance == 3 ~ 0, 
    dont_give_eqchance == 4 ~ -0.5, 
    dont_give_eqchance == 5 ~ -1, 
    dont_give_eqchance %in% c(8,9) ~ NA_real_
  )) %>% 
  mutate(treateq_few_prob = case_when( 
    treateq_few_prob == 1 ~ 1, 
    treateq_few_prob == 2 ~ 0.5, 
    treateq_few_prob == 3 ~ 0, 
    treateq_few_prob == 4 ~ -0.5, 
    treateq_few_prob == 5 ~ -1, 
    treateq_few_prob %in% c(8,9) ~ NA_real_
  )) %>%
  mutate(eq_rights_toofar = case_when(
    eq_rights_toofar == 1 ~ -1, 
    eq_rights_toofar == 2 ~ -0.5, 
    eq_rights_toofar == 3 ~ 0, 
    eq_rights_toofar == 4 ~ 0.5, 
    eq_rights_toofar == 5 ~ 1, 
    eq_rights_toofar %in% c(8,9) ~ NA_real_
  )) %>% 
  mutate(worried_less_eq = case_when( 
    worried_less_eq == 1 ~ -1, 
    worried_less_eq == 2 ~ -0.5, 
    worried_less_eq == 3 ~ 0, 
    worried_less_eq == 4 ~ 0.5, 
    worried_less_eq == 5 ~ 1, 
    worried_less_eq %in% c(8,9) ~ NA_real_
  )) %>%
  mutate(bigprob = case_when(
    bigprob == 1 ~ -1, 
    bigprob == 2 ~ -0.5,
    bigprob == 3 ~ 0,
    bigprob == 4 ~ 0.5,
    bigprob == 5 ~ 1,
    bigprob %in% c(8,9) ~ NA_real_
  ))

mydata$egal <- rowMeans(mydata[, c("worried_less_eq", "eq_rights_toofar", 
                                   "treateq_few_prob", "dont_give_eqchance", "eq_opp_succeed","bigprob")])

```

```{r, echo = FALSE}
# two primary dep. vars - opinion on Africa sanctions and actual opinon
## know_africa = binary for whether one takes a position on Africa sanctions
## africa_sanct = actual opinion on Sanctions

# takes opinion on alternate dep. variables
mydata <- mydata %>%
    mutate(op_govt_services = case_when( 
      govt_services == 9 ~ NA_real_, 
      govt_services %in% c(0,8) ~ 0, 
      govt_services %in% c(1:7) ~ 1
    )) %>%
    mutate(op_import_restr = ifelse(mydata$import_restr == 1, 1, 
    ifelse(mydata$import_restr %in% c(5, 8), 0, NA))) %>%
    mutate(op_coop_russia = case_when(
      coop_russia == 9 ~ NA_real_,
      coop_russia %in% c(0,8) ~ 0, 
      coop_russia %in% c(1:7) ~ 1
    )) %>%
    mutate(op_defense_spend = case_when(
      defense_spend == 9 ~ NA_real_,
      defense_spend %in% c(0,8) ~ 0, 
      defense_spend %in% c(1:7) ~ 1
    )) %>%
    mutate(op_interv_ca = case_when( 
      interv_ca == 9 ~ NA_real_,
      interv_ca %in% c(0,8) ~ 0, 
      interv_ca %in% c(1:7) ~ 1
    ))

```

```{r, echo=FALSE}
# generate summary statistics
alt_dep <- c("op_govt_services","op_import_restr","op_defense_spend","op_interv_ca","op_coop_russia")
summary_stats <- lapply(mydata[alt_dep], summary)
frequencies <- lapply(mydata[alt_dep], table)

# print summary statistics
for (i in seq_along(summary_stats)) {
  cat("Frequencies for", alt_dep[i], ":\n")
  print(frequencies[i])
  cat("\n")
  
  cat("Summary Statistics for", alt_dep[i], ":\n")
  print(summary_stats[i])
  cat("\n")
}

```

### 1) Opinion on sanctions, non-hispanic whites
```{r}
# non-hispanic whites, form A
white_form_a <- mydata %>% filter(white == 1 & form_a == 1)
table(white_form_a$sanctions)

# whites, formed an opinion = 1, haven't = 0, form B
table(white_form_a$op_africa)

# non-hispanic whites, form B
white_form_b <- mydata %>% filter(white == 1 & form_b == 1)
table(white_form_b$sanctions)

# whites, formed an opinion = 1, haven't = 0, form B
table(white_form_b$op_africa)

# non-hispanic whites, form A and B
white_both_forms <- mydata %>% filter(white == 1)
table(white_both_forms$sanctions)

# whites, formed an opinion = 1, haven't = 0, form A+B
table(white_both_forms$op_africa)
```

### 2) Frequencies for Black Americans
```{r}
# Black Americans, form A
black_form_a <- mydata %>% filter(black == 1 & form_a == 1)
table(black_form_a$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form A
table(black_form_a$op_africa)

# Black Americans, form B
black_form_b <- mydata %>% filter(black == 1 & form_b == 1)
table(black_form_b$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form B
table(black_form_b$op_africa)

# Black Americans, form A and B
black_both_forms <- mydata %>% filter(black == 1)
table(black_both_forms$sanctions)

# Black Americans, formed an opinion = 1, haven't = 0 , form A+B
table(black_both_forms$op_africa)

```

### 3) Accounting for No Opinion Model
**Non-hispanic whites, form A and B**
```{r, echo=FALSE}
# create models for all specifications 
part3_1 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_both_forms)
part3_2 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_form_a)
part3_3 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = white_form_b)
part3_4 <-  glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college, family = binomial(link = "probit"), 
             data = black_both_forms)
summary(part3_1)

```
**Non-hispanic whites, form A**
```{r, echo=FALSE}
summary(part3_2)
```
**Non-hispanic whites, form B**
```{r, echo=FALSE}
summary(part3_3)
```
**Black Americans, forms A and B**
```{r, echo=FALSE}
summary(part3_4)
```

### 4) Accounting for no opinion with racial resentment
```{r}
part4_1 <- glm(op_africa ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = white_form_b)
summary(part4_1)
```

### 5) Identical model, alternative outcomes
```{r, echo = FALSE}
part5_1 <- glm(op_defense_spend ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_2 <- glm(op_interv_ca ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_3 <- glm(op_govt_services ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_4 <- glm(op_coop_russia ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
part5_5 <- glm(op_import_restr ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata)
```
**Defense spending:**
```{r}
summary(part5_1)
```
**Intervention in Central America:**
```{r}
summary(part5_2)
```
**Government services/cuts in spending:**
```{r}
summary(part5_3)
```
**Cooperate with Russia:**
```{r}
summary(part5_4)
```
**Import Restrictions:**
```{r}
summary(part5_5)
```

### 6) Accounting for opposition
**Equal Opportunity Variable Descriptives **
Histogram is in the zip, file name is "egalitarian.png"
```{r}
#alpha(mydata, "eq_opp_succeed", "treateq_few_prob", "dont_give_eqchance", "eq_rights_toofar", "worried_less_eq", "bigprob", na.rm = T)
summary(mydata$egal) # Descriptive Statistics

```

**Frequencies for Party ID Variable**
```{r} 
table(mydata$party_id)
```

**Basic Model **
```{r}
part6 <- glm(sanctions ~ racism + egal + party_id, family = binomial(link = "probit"), data = mydata)
summary(part6)
```


**Same Model, Alternate Egalitarian Variable **
```{r}
# Construct alternate version of egalitarian variable
mydata$egal_alt <- rowMeans(mydata[, c("bigprob","eq_opp_succeed")])

# Descriptive Statistics 
summary(mydata$egal_alt)

# Identical mode, with alternate egalitarian variable
part6_alt <- glm(sanctions ~ racism + egal_alt + party_id, family = binomial(link = "probit"), data = mydata)
summary(part6_alt)
```

The histogram is in the zip, file name is "egalitarian_alt.png"

**Accounting for biological racism **
```{r, echo = FALSE}
# Generate variable for biological racism
mydata <- mydata %>%
  mutate(racism_bio = case_when(
    racism_bio %in% c(8,9,0) ~ NA_real_,
    racism_bio == 1 ~ 1,
    racism_bio == 2 ~ 0.5,
    racism_bio == 3 ~ 0,
    racism_bio == 4 ~ -0.5,
    racism_bio == 5 ~ -1
  ))

# Bio racism in place of modern racism
part6_b <- glm(sanctions ~ racism_bio + egal + party_id, family = binomial(link = "probit"), data = mydata)
part6_c <- glm(sanctions ~ racism + racism_bio + egal + party_id, family = binomial(link = "probit"), data = mydata)

```

```{r} 
# Frequencies for biological racism
table(mydata$racism_bio)

# Biological racism in place of modern racism
summary(part6_b)

# Biological racism in addition to modern racism
summary(part6_c)
```

### 7) Additional Race Items
```{r, echo = FALSE}
# New race items 
mydata <- mydata %>% 
  mutate(int_op = case_when( # takes an opinion on school integration
    int_op %in% c(8,9,0) ~ NA_real_,
    int_op == 1 ~ 1,
    int_op == 5 ~ 0
  )) %>% 
  mutate(integration = case_when( # 1 = supports integration, 0 = doesn't/depends
    integration %in% c(8,9,0) ~ NA_real_,
    integration == 1 ~ 1,
    integration %in% c(5,7) ~ 0
  )) %>% 
  mutate(workplace_op = case_when( # takes an opinion on workplace discrimination
    workplace %in% c(1,5) ~ 1,
    workplace %in% c(0,9) ~ 0
  )) %>%
  mutate(workplace = case_when( # views on workplace discrimination
    workplace %in% c(8,9,0) ~ NA_real_,
    workplace == 1 ~ 1,
    workplace == 2 ~ 0.666,
    workplace == 4 ~ 0.333,
    workplace == 5 ~ 0
  )) 

# takes an opinion on special effort
mydata$effort_poc_op <- rep(NA, length(nrow(mydata)))
mydata$effort_black_op <- rep(NA, length(nrow(mydata)))
mydata <- mydata %>%
  mutate(effort_poc_op = case_when(
    effort_poc %in% c(1,7) ~ 1,
    effort_poc %in% c(8,0) ~ 0,
    effort_poc == 9 ~ NA_real_
  )) %>%
  mutate(effort_black_op = case_when(
    effort_black %in% c(1,7) ~ 1,
    effort_black %in% c(8,0) ~ 0,
    effort_black == 9 ~ NA_real_
  ))

# efforts for POCs and Black Americans, respectively
mydata$effort_poc <- ifelse(mydata$effort_poc %in% c(8, 9, 0), NA, mydata$effort_poc)
mydata$effort_black <- ifelse(mydata$effort_black %in% c(8, 9, 0), NA, mydata$effort_black)
```

**Frequencies for alternate race items**

```{r}
# Function to calculate frequencies based on conditions for multiple variables
calculate_frequencies <- function(data, conditions) {
  results <- list()
  
  for (variable in names(conditions)) {
    result_white <- table(data[data$white == 1, variable])
    result_black <- table(data[data$black == 1, variable])
    
    results[[paste("freq_", variable, "_white", sep = "")]] <- result_white
    results[[paste("freq_", variable, "_black", sep = "")]] <- result_black
  }
  
  return(results)
}

# Define conditions for each variable
conditions <- list(
  effort_poc = 1,
  effort_poc_op = 1,
  effort_black = 1,
  effort_black_op = 1,
  workplace = 1,
  workplace_op = 1,
  integration = 1,
  int_op = 1
)

# Generate frequencies for all variables
frequencies <- calculate_frequencies(mydata, conditions)

# Display the results
cat("\nFrequencies for each value of each variable if white == 1:\n")
for (variable in names(frequencies)) {
  cat(paste(variable, ":\n"))
  print(frequencies[[variable]])
  cat("\n")
}
```

**Re-doing part 4 with alternate race variables**
```{r}
part7_1 <- glm(int_op ~ knowledge + taste + sex + less_hs + hs + somecol +
               college + racism, family = binomial(link = "probit"), 
             data = mydata) # takes a position on integration

part7_2 <- glm(workplace_op ~ knowledge + taste + sex + less_hs + hs + somecol +
                            college + racism, family = binomial(link = "probit"), 
                          data = mydata) # takes a position on workplace

# Takes an position on school integration
summary(part7_1)

# Takes a position on workplace discrimination
summary(part7_2)
```
I see that there's an issue with the second model, where the dependent variable is whether
the respondent took a position on the government ending workplace discrimination. I haven't
quite been able to figure out why this is, but I ran the model with one predictor
variable at a time, and the modern racism variable is the one that breaks it:

```{r}
part7_2_alt <- glm(workplace_op ~ knowledge + taste + sex + less_hs + hs + somecol +
                 college, family = binomial(link = "probit"), 
               data = mydata) # takes a position on workplace

summary(part7_2_alt)
```

I have limited experience in problem-solving this specific type of issue, but I think
another type of logistic regression may have to be used to reach convergence, otherwise
there is something off with the modern racism variable.

**Re-doing part 6 with alternate race variables **
At the time of writing, I cannot get the model for workplace discrimination or special efforts for Black Americans to converge. I also changed the special efforts model to use OLS rather than probit since the dependent variable is continuous with $y \in [1, 7]$.
```{r}
# Opinion on school integration
part7_i <- glm(integration ~ racism + egal + party_id, family = binomial(link = "probit"), 
               data = mydata)
summary(part7_i)

# Opinion on effort for all people of color
part7_j <- lm(effort_poc ~ racism + egal + party_id, data = mydata)
summary(part7_j)

```
**Correlation Items**
```{r}
# Correlation Tasks
# Opinion on apartheid and opinion on school integration
cor(mydata$op_africa, mydata$int_op, method = "pearson", use = "complete.obs")

# Opinion on apartheid and opinion on workplace discrimination
cor(mydata$op_africa, mydata$workplace_op, method = "pearson", use = "complete.obs")

# Opinion on apartheid and opinion on special efforts for POCs
cor(mydata$op_africa, mydata$effort_poc_op, method = "pearson", use = "complete.obs")

# Opinion on apartheid and opinion on special efforts for Black Americans
cor(mydata$op_africa, mydata$effort_black_op, method = "pearson", use = "complete.obs")
```

